---
name: Matt Lloyd Jones
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA, PhD
address: he/him
profilepic: mattlloydjones.jpg
#website: 
github: befriendabacterium
#linkedin: 
#twitter: 
headcolor: 414141
output: vitae::awesomecv
docname: CV made with `vitae` R package
---

```{r setup, include=FALSE}
#this CV was made using the very helpful instructions of Mitchell O'Hara-Wild for using vitae:
#https://ropensci.org/blog/2019/01/10/vitae/ 
#https://www.r-bloggers.com/2019/01/vitae-dynamic-cvs-with-r-markdown/
#the instructions for using rorcid come from:
#https://ciakovx.github.io/rorcid.html


knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
#remotes::install_github("ropensci/rorcid@api-v3")
library(vitae)
library(rorcid)
library(scholar)
library(tidyverse)

#authorise rorcid - UNCOMMENT TO AUTHORISE AND GET YOUR ACCESS TOKEN TO PUT IN .Renviron - see https://ciakovx.github.io/rorcid.html
#rorcid::orcid_auth()

```

# Professional Summary

I am a researcher who is passionate about making the most of research already conducted and improving the rigour and transparency of research yet to be conducted. Having started out my research career in human geography as an undergraduate and subsequently moved on to a laboratory-based PhD in microbial ecology, I have a practical appreciation and understanding of the hard work that goes into conducting primary research in science as well as social science and the humanities. I now seek to maximise the accessibility and usefulness of primary research for researchers and non-researchers alike, offering my programming and statistical skills towards a combination of evidence synthesis, study design and analysis, and teaching others robust and transparent research methods.

<!-- As an evidence synthesist working in systematic review and meta-analysis, I enjoy the challenge of piecing together different bits of research to try to answer big research questions more conclusively. This requires me to apply my acute understanding of study designs and their biases, as well as my extensive computational and statistical skills. Nonetheless, this process of attempting to synthesise research also often peels back its curtain - revealing how lack of rigour and transparency frequently creeps in to prevent research from achieving its purported goals. Whilst we are all to some extent subject to the systems of which we are part, I try to overcome these issues in my own research through statistically-informed design and analysis, alongside adopting open research practices such as preregistration, preprinting and data and code sharing. These are also values that I advocate for and train to other researchers through my teaching, mentoring, talks and involvement in open research-focussed initiatives. -->


# Education & qualifications

## Education

```{r edu, include=TRUE}
#pull education data from orcid
orcid_education<-rorcid::orcid_educations('0000-0001-5841-4554')$`0000-0001-5841-4554`$`affiliation-group`$summaries
#join into one dataframe
orcid_education<-orcid_education %>% purrr::reduce(full_join)

#convert month numbers to abbrevs
orcid_education$`education-summary.start-date.month.value`<-month.abb[as.numeric(orcid_education$`education-summary.start-date.month.value`)]
orcid_education$`education-summary.end-date.month.value`<-month.abb[as.numeric(orcid_education$`education-summary.end-date.month.value`)]

#replace NA with present for end year
orcid_education$`education-summary.end-date.year.value`[is.na(orcid_education$`education-summary.end-date.year.value`)]<-'present'
#replace NA with present for end year
orcid_education$`education-summary.end-date.month.value`[is.na(orcid_education$`education-summary.end-date.month.value`)]<-''

#print detailed entries
vitae::detailed_entries(orcid_education,
     what = `education-summary.role-title`,
     when = paste(`education-summary.start-date.month.value`,`education-summary.start-date.year.value`,
                  '-',
                  `education-summary.end-date.month.value`,`education-summary.end-date.year.value`),
     with = paste(`education-summary.department-name`,`education-summary.organization.name`, sep=', '),
     where = `education-summary.organization.address.city`
    # # why = cites
   )
```

## Qualifications

```{r qual, include=TRUE}
#pull qualification data from orcid
orcid_qualification<-rorcid::orcid_qualifications('0000-0001-5841-4554')$`0000-0001-5841-4554`$`affiliation-group`$summaries
#join into one dataframe
orcid_qualification<-orcid_qualification %>% purrr::reduce(full_join)

#convert month numbers to abbrevs
orcid_qualification$`qualification-summary.start-date.month.value`<-month.abb[as.numeric(orcid_qualification$`qualification-summary.start-date.month.value`)]
orcid_qualification$`qualification-summary.end-date.month.value`<-month.abb[as.numeric(orcid_qualification$`qualification-summary.end-date.month.value`)]

#replace NA with present for end year
orcid_qualification$`qualification-summary.end-date.year.value`[is.na(orcid_qualification$`qualification-summary.end-date.year.value`)]<-'present'
#replace NA with present for end year
orcid_qualification$`qualification-summary.end-date.month.value`[is.na(orcid_qualification$`qualification-summary.end-date.month.value`)]<-''

#print detailed entries
vitae::detailed_entries(orcid_qualification,
     what = `qualification-summary.role-title`,
     when = paste(`qualification-summary.start-date.month.value`,`qualification-summary.start-date.year.value`,
                  '-',
                  `qualification-summary.end-date.month.value`,`qualification-summary.end-date.year.value`),
     with = paste(`qualification-summary.department-name`,`qualification-summary.organization.name`, sep=', '),
     where = `qualification-summary.organization.address.city`
    # # why = cites
   )
```

# Employment

```{r emp, include=TRUE}

orcid_employment<-rorcid::orcid_employments('0000-0001-5841-4554')$`0000-0001-5841-4554`$`affiliation-group`$summaries

orcid_employment<-orcid_employment %>% purrr::reduce(full_join)

#convert month numbers to abbrevs
orcid_employment$`employment-summary.start-date.month.value`<-month.abb[as.numeric(orcid_employment$`employment-summary.start-date.month.value`)]
orcid_employment$`employment-summary.end-date.month.value`<-month.abb[as.numeric(orcid_employment$`employment-summary.end-date.month.value`)]

#replace NA with present for end year
orcid_employment$`employment-summary.end-date.year.value`[is.na(orcid_employment$`employment-summary.end-date.year.value`)]<-'present'
#replace NA with present for end year
orcid_employment$`employment-summary.end-date.month.value`[is.na(orcid_employment$`employment-summary.end-date.month.value`)]<-''

#print detailed entries
vitae::detailed_entries(orcid_employment,
     what = `employment-summary.role-title`,
     when = paste(`employment-summary.start-date.month.value`,`employment-summary.start-date.year.value`,
                  '-',
                  `employment-summary.end-date.month.value`,`employment-summary.end-date.year.value`),
     with = paste(`employment-summary.department-name`,`employment-summary.organization.name`, sep=', '),
     where = `employment-summary.organization.address.city`,
    # # why = cites
   )

```


# Skills

## Statistics & programming

-   **10 years** experience in parametric statistics and non-parametric statistics including power analysis, linear models, generalised linear mixed models, ordination and machine learning techniques.

-   **10 years** experience programming in R including statistics, figure production, data wrangling, text processing and web scraping/web APIs.

-   **\>2 years** experience in document markup in RMarkdown Markdown, Quarto and LaTeX - including for the production of PDF and Word documents, website content and presentations. This CV was produced using `rmarkdown` and the `vitae` package!

-   **2 years** experience in interactive dashboard development in RShiny

-   **3 years** experience in using git and GitHub for version control for academic research projects and software development

-   Learning UNIX and python programming

## Evidence synthesis (systematic review & meta-analysis)

-   **Protocol design** and **pre-registration**

-   **Systematic searching** (e.g. search design; processing bibliographic data in R)

-   **Study screening** (e.g. in Rayyan and R)

-   **Data extraction, wrangling and standardisation** (e.g. extraction from plots; individual participant data processing; effect size calculation)

-   **Meta-analytical modelling** (e.g. fixed, random & mixed effects models; repeated measures designs; sensitivity analyses)

-   Systematic review **project management** (e.g. training, task allocation)

## Other

-   **Bioinformatics** in UNIX and R (e.g. QIIME, DADA2)

-   **Laboratory experience** (e.g. culture-based techniques, molecular biology, amplicon sequencing, spectrophotometry, flow cytometry, robotic pipetting, microscopy, tissue culture, field sampling and processing.

-   **Ethics applications** for research (including obtaining approval from Medical School research ethics committees)

-  **Project management** techniques (e.g. Sprint, kanban, research-specific techniques)

<!-- - **Spanish language** (beginner-to-intermediate level speaking and writing) -->

# Teaching/training experience

-   **On-the-job supervision and training** of PhD students and national and international collaborators in statistics, R programming and evidence synthesis (2019-present; University of Exeter)

-   **Delivery of workshops on open research practices** including preregistration, preprinting, and code and data sharing as part of the UKRN's 'Train the Trainer' programme and Exeter Data Analytics Hub (Summer 2023; University of Exeter)

-   **Teaching and assessment of medical students** on 2 Special Study Units (SSUs) on AMR in the environment (February and December 2021; University of Exeter)

-   **Formal supervision of two Master's student projects** who both achieved Merits (2015-2017; Imperial College London)

-   **Teaching of Master's and undergraduate course content** including statistics and R programming, molecular biology, field ecology, population genetics (2014-2017; Imperial College London)

# Membership and service

## Membership

```{r mem, include=TRUE}
orcid_memberships<-rorcid::orcid_memberships('0000-0001-5841-4554')$`0000-0001-5841-4554`$`affiliation-group`$summaries
orcid_memberships<-orcid_memberships %>% purrr::reduce(full_join)

#convert month numbers to abbrevs
orcid_memberships$`membership-summary.start-date.month.value`<-month.abb[as.numeric(orcid_memberships$`membership-summary.start-date.month.value`)]
orcid_memberships$`membership-summary.end-date.month.value`<-month.abb[as.numeric(orcid_memberships$`membership-summary.end-date.month.value`)]

#replace NA with present for end year
orcid_memberships$`membership-summary.end-date.year.value`[is.na(orcid_memberships$`membership-summary.end-date.year.value`)]<-'present'
#replace NA with present for end year
orcid_memberships$`membership-summary.end-date.month.value`[is.na(orcid_memberships$`membership-summary.end-date.month.value`)]<-''

#print detailed entries
vitae::detailed_entries(orcid_memberships,
     what = `membership-summary.role-title`,
     when = paste(`membership-summary.start-date.month.value`,`membership-summary.start-date.year.value`,
                  '-',
                  `membership-summary.end-date.month.value`,`membership-summary.end-date.year.value`),
     with = `membership-summary.organization.name`,
     where = `membership-summary.organization.address.city`,
    # # why = cites
   )

```

## Service

```{r ser, include=TRUE}
orcid_services<-rorcid::orcid_services('0000-0001-5841-4554')$`0000-0001-5841-4554`$`affiliation-group`$summaries
orcid_services<-orcid_services %>% purrr::reduce(full_join)

#convert month numbers to abbrevs
orcid_services$`service-summary.start-date.month.value`<-month.abb[as.numeric(orcid_services$`service-summary.start-date.month.value`)]
orcid_services$`service-summary.end-date.month.value`<-month.abb[as.numeric(orcid_services$`service-summary.end-date.month.value`)]

#replace NA with present for end year
orcid_services$`service-summary.end-date.year.value`[is.na(orcid_services$`service-summary.end-date.year.value`)]<-'present'
#replace NA with present for end year
orcid_services$`service-summary.end-date.month.value`[is.na(orcid_services$`service-summary.end-date.month.value`)]<-''

#print detailed entries
vitae::detailed_entries(orcid_services,
     what = `service-summary.role-title`,
     when = paste(`service-summary.start-date.month.value`,`service-summary.start-date.year.value`,
                  '-',
                  `service-summary.end-date.month.value`,`service-summary.end-date.year.value`),
     with = `service-summary.organization.name`,
     where = `service-summary.organization.address.city`,
    # # why = cites
   )

```


# Talks

```{r talks, include=TRUE}

# #FROM ORCID
orcid_talks<-rorcid::orcid_works('0000-0001-5841-4554')$`0000-0001-5841-4554`$works
orcid_talks<-orcid_talks[orcid_talks$type=='lecture-speech',]
orcid_talks$`publication-date.month.value`<-month.abb[as.numeric(orcid_talks$`publication-date.month.value`)]

vitae::detailed_entries(orcid_talks,
     # what = 
     when = paste(`publication-date.day.value`,`publication-date.month.value`,`publication-date.year.value`),
     with = title.title.value,
     where = `journal-title.value`
     #why = cites
)

```
# Distinctions

```{r dis, include=TRUE}
orcid_distinctions<-rorcid::orcid_distinctions('0000-0001-5841-4554')$`0000-0001-5841-4554`$`affiliation-group`$summaries
orcid_distinctions<-orcid_distinctions %>% purrr::reduce(full_join)

#convert month numbers to abbrevs
orcid_distinctions$`distinction-summary.start-date.month.value`<-month.abb[as.numeric(orcid_distinctions$`distinction-summary.start-date.month.value`)]


#print detailed entries
vitae::detailed_entries(orcid_distinctions,
     what = `distinction-summary.organization.name`,
     when = paste(`distinction-summary.start-date.month.value`,`distinction-summary.start-date.year.value`),
     with = `distinction-summary.role-title`,
     where = `distinction-summary.organization.address.city`,
    # # why = cites
   )

```


# Funding awarded

```{r fun, include=TRUE}
orcid_funding<-rorcid::orcid_fundings('0000-0001-5841-4554')$`0000-0001-5841-4554`$group$`funding-summary`
orcid_funding<-orcid_funding %>% purrr::reduce(full_join)
#sort by year
orcid_funding<-orcid_funding[order(orcid_funding$`end-date.year.value`,decreasing = T),]

#convert month numbers to abbrevs
orcid_funding$`start-date.month.value`<-month.abb[as.numeric(orcid_funding$`start-date.month.value`)]
orcid_funding$`end-date.month.value`<-month.abb[as.numeric(orcid_funding$`end-date.month.value`)]

#replace NA with present for end year
orcid_funding$`end-date.year.value`[is.na(orcid_funding$`end-date.year.value`)]<-'present'
#replace NA with present for end year
orcid_funding$`end-date.month.value`[is.na(orcid_funding$`end-date.month.value`)]<-''

#print detailed entries
vitae::detailed_entries(orcid_funding,
     what = title.title.value,
     when = paste(`start-date.month.value`,`start-date.year.value`,
                  '-',
                  `end-date.month.value`,`end-date.year.value`),
     with = organization.name,
     where = c("£196,760","£5000")
    # why = cites
   )


```



# Publications

```{r scholarscrape, include=TRUE}

# # #FROM ORCID
# orcid_pubs<-rorcid::orcid_works('0000-0001-5841-4554')$`0000-0001-5841-4554`$works
# orcid_pubs<-orcid_pubs[orcid_pubs$type=='journal-article',]
# vitae::detailed_entries(orcid_pubs,
#      what = title.title.value,
#      when = `publication-date.year.value`,
#      #with = `source.assertion-origin-name.value`,
#      where = `journal-title.value`
#      #why = cites
# )

#FROM SCHOLAR
scholar_pubs<-scholar::get_publications("MgeozOEAAAAJ")
#reorder by year
scholar_pubs<-scholar_pubs[order(scholar_pubs$year, decreasing = T),]

```

## In prep

```{r pre, include=TRUE}

scholar_pubs_preprinted<-scholar_pubs[scholar_pubs$journal=='bioRxiv',]
#restrict to this year's preprints
scholar_pubs_preprinted<-scholar_pubs_preprinted[scholar_pubs_preprinted$year==2023,]

#manually add my in prep work
scholar_pubs_preprinted[2,]<-NA
scholar_pubs_preprinted$author[2]<-'ML Jones, A Bethel, A. Peralta, A. Leonard, MP Quiroga, J Dominguez, N Casanova, M Fernández-Miyakawa, A Sanchez-Tojar, A Petroni, W Gaze, R Garside'
scholar_pubs_preprinted$year[2]<-'2023'
scholar_pubs_preprinted$journal[2]<-'In prep'
scholar_pubs_preprinted$title[2]<-'A systematic review of the relationship between antibiotic use and resistance in beef farming'

#reverse order so next coming at top
scholar_pubs_preprinted<-scholar_pubs_preprinted[rev(1:nrow(scholar_pubs_preprinted)),]

#print detailed entries
vitae::detailed_entries(scholar_pubs_preprinted,
     what = author,
     when = year,
     with = title,
     where = journal
    # why = cites
   )
```

## Published

```{r pub, include=TRUE}

scholar_pubs_published<-scholar_pubs[scholar_pubs$journal!='bioRxiv',]
#for the Frontiers in Vet Sci pub, fill in the rest of the authors manually
scholar_pubs_published$author[scholar_pubs_published$number=='10, 1079948']<-'ML Jones, MS Barnish, RR Hughes, AK Murray, O Mansour, T Loni, HM Vickery, ML Evans, L Green, N Verdezoto'

#print detailed entries
vitae::detailed_entries(scholar_pubs_published,
     what = author,
     when = year,
     with = title,
     where = journal
    # why = cites
   )

```
